%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}

\setlength{\parskip}{5pt}%
\setlength{\parindent}{0pt}%

Completing a PhD is a singular achievement but also one impossible to achieve alone.

I must first thank my co-advisors, Luis Ceze and Mark Oskin.
To be coadvised is to be paired with two indefatigable champions with no clear model for consensus.
Luis taught me to be ambitious in research impact and aggressive with my creativity.
Mark taught me to be discriminating in idea selection and lighthearted in my daily work.
The act of balancing their unending ideas and criticism has shaped the mold of my research forever.
Thank you for advising me!

Like any PhD student at the Allen School for Computer Science, I had not only two advisors but also a cabal of faculty and industry researchers helping me along.
Notably, Magda Balazinska taught me how to lift architecture research into the world of systems and how to lead research collaborations with thoughtfulness and clarity.
Other mentors improved my work through significant revision, feedback, entropy, and expertise: Jon Barron, Alvin Cheung, David Gallup, Warren Hunt, Anton Kaplanyan, Visvesh Sathe, Steve Seitz.

Much as I tried to conduct a research project without anyone's help, I could not have completed a single page of this dissertation without my friends and lab mates: Armin Alaghi, Meghan Cowan, Maureen Daum, Emily Furst, Brandon Haynes, Brandon Holt, Sung Kim, Vincent Lee, Ming Liu, Liang Luo, Thierry Moreau, Brandon Myers, Jacob Nelson, Benjamin Ransford, Adrian Sampson, Pratyush Patel, Luis Vega, Mark Wyse, Eddie Yan. Very special thanks to my friends Kira Goldner, Ellie Levey, Lucy Lin, and Maarten Sap for providing company at a fortifying brunch as necessary.

Preparing a dissertation may be hard, but running the operations that allow research to be researched and innovation to be innovated is much harder. None of my work could be possible without the emotional and infrastructural support of Elise Dorough, Melody Kadenko, Amanda Robles, and Anna Wehovsky.

My arrival at the University of Washington would not have occurred without a cosmic alignment of advising from faculty at Columbia University: Steven Edwards, Martha Kim, and Shree Nayar. The CRA-W's DREU program connected me to Iris Bahar at Brown University, my first guide through computer engineering.

I am grateful to the staff of High Technology High School for introducing me to research, and Gary S. Settles for being my first faculty mentor. My original education on abstraction and interfaces came from a decade of piano lessons from Beth S. Chen.

Finally, thank you to my parents, Rekha Datta and Subrata Mazumdar, for supporting me in a great many things but especially this process.

No level of thanks could possibly be sufficient to account for Gregory T. Woolston's contribution to this work; I will not even begin to try.

\endgroup
